Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-01-16 writeups/proposal/proposal.tex
foo
Former-commit-id: c04fca3ad06f7d84f695a57829666dd6f6798401 [formerly 4332a89b0b3acf3ed9541be8039aae759fce0d6e]
Former-commit-id: 3a19506cf90af2263411a2d7e63f6667c2feb50d

The ACT-R cognitive architecture \parencite{Anderson2004} contains one of the leading theories of human declarative memory.
The declarative memory component in ACT-R is a Bayesian statistical model.
This is the same type of co-occurrence Naive Bayes statistical model that is prominent in the more general machine-learning field.
When these Bayesian models are used for machine learning, it is common to use a large number of observations to construct the co-occurrence matrix that is the foundation for the model.
The primary reason for this is that the stability of statistical models increase as sample size increases.

However it is much less common in the cognitive modeling community to use a large number of observations to build up declarative memory when creating ACT-R models.
If a cognitive modeler is using the declarative memory component of ACT-R,
it is common to either construct the co-occurrences by hand, or use a small training set of data to initially build up the declarative memory system.
This approach can and has worked well.
Essentially the modeler is only including the observations in declarative memory that are relevant to the specific task that they are studying.

@@

The work for this proposal will expand on the knowledge gained from previous work that has tested retrieval models on large-scale datasets.
It will focus specifically on how two state-of-the-art declarative memory retrieval models (ACT-R Bayesian and random permutations) can be improved further, by testing these models on two real-world tagging tasks.
One primary objective is to compare the random-permutation vector-based model to ACT-R's declarative memory theory when the datasets used for each model contain hundreds of millions to billions of data points.
Another objective is to test how much improvement is gained by incorporating the strengths of each model into the other (i.e., modifying model components).
For example, it is currently unexplored how a vector-based model can be modified to retrieve results that are based not only on context, but also on the prior odds that a particular item in memory will be needed again.
Since large datasets will be used, a rich volume of data will be available to test the models.
This enables constraints and assumptions for each theory to be rapidly tested and new model components to be hypothesized and quickly evaluated.

@@

These hashtags relate to a user's goals and interests because they are a form of human-based document tagging \parencite{Chang2010}.
Further, people are using hashtags as a way to create information streams on social media sites \parencite{Kwak2010}.
Twitter users, for example, commonly create and use hashtags for upcoming political events that interest them, such as debates and races \parencite{Diakopoulos2010}.
So if we can predict what hashtags a user is interested in, we have a better understanding of the information streams that they care about.
With that understanding, we can tailor the system to suggest hashtags that they may not yet know about but are of likely interest to them.
We can help aid in their discovery of fresh and relevant information that match their goals on the site.

@@

Alongside testing these memory retrieval models on Twitter hashtag use, they will also be tested on tag use for StackOverflow posts.
StackOverflow is a question and answer site for computer programming where users ask programming-related questions and fellow members of the community provide answers.
A user with a programming-related question creates a post with their question and tags the post with a few specific programming-related tags. 
User-chosen tags on the StackOverflow site represent the primary topic of the question, such as a specific programming language, tool, software package, or framework.
Some example tags for StackOverflow are \emph{PHP}, \emph{Arrays}, \emph{MVC}, \emph{C\#}, and \emph{Common Lisp}.

@@

ACT-R's declarative memory system places strong constraints on how a user's prior knowledge and experience influences the likelihood that a particular memory item is retrieved \parencite{Anderson2004}.
This decay rate equation formalizes how recency and frequency of hashtag use relate to the prior probability that a hashtag will be retrieved.
However, it is unexplored how a user's prior knowledge should influence retrieval for vector-based models.
I will explore how a user's prior knowledge influences the likelihood that a particular hashtag is chosen for both ACT-R's memory theory and vector-based models.

@@

A user's prior hashtag use will be an essential model component for domains such as Twitter, where the number of possible hashtags is practically infinite.
In these domains, the model can utilize a user's hashtag history as a way to prune the infinite space of possible hashtags, and generate a much smaller and more manageable set for prediction.
However, not only should the model properly take into account a user's prior hashtag use, but it should also generate new hashtag predictions when a user is most likely choosing a hashtag they have never used before.
The end goal is to have a model that can properly balance the user's tag history with the contextual cues in the post in order to generate an accurate prediction.

@@

ACT-R \parencite{Anderson2004} is a cognitive architecture that formalizes how each cognitive process of the brain (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of that architecture that models the timing, learning, and forgetting processes that make up long-term declarative memory retrieval.
The equations that make up this system can be derived through a rational analysis of long-term memory retrieval.
That is, given the task of retrieving a chunk of information from long-term declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likelihood of needing retrieval again, given the prior history of exposure to the chunk.
These chunk prior probabilities are then adjusted for the current context, so that the posterior probabilities represent the likelihood that a chunk is needed, given prior odds and adjusted by current environment state.

@@

Usually information is lost when the data are restructured into a smaller set of latent dimensions.
However it was shown that this process actually improves prediction and reduces noise by allowing the frequency count of highly similar concepts (words) to be pooled together and represented by a single dimension.
\textcite{Landauer1997} tested the LSA model on the Test of English as a Foreign Language (TOEFL) task of choosing the best of four possible synonyms to a target word.
Model results were on par with a large sample of applicants to american universities from non-English speaking countries (64.4\% compared to 64.5\%).
Model performance also improved when the original dimensionality of the data was reduced, but only up to a point.
Afterwards further reductions in the dimensionality of the data began to degrade performance.

@@

For vector-based systems, each word is represented by an environment vector $e_{i}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix, which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from bag-of-words co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

More specific hashtag-recommendation models that attempt to predict a user's chosen hashtag have also been created and tested for a few social media sites.
Google has even deployed a hashtag-recommendation model to help users properly tag posts on their Google+ social media site \parencite{GoogleKeynote2013}.
A tag-suggestion tool has also been deployed for the \url{http://tex.stackexchange.org} and \url{http://superuser.com} StackExchange sites.
Models for Twitter and StackOverflow have also been proposed and tested, but none have yet been deployed.

@@

\textcite{Stanley2013}'s model was based on ACT-R's declarative memory retrieval theory, which at the core is also a Bayesian co-occurrence model.
However several modifications to the model were made from the standard Bayesian ACT-R declarative memory theory, so it was more sophisticated than the standard ACT-R model and the model used by \textcite{Kuo2011}.
\citeauthor{Stanley2013} used a data-driven entropy weighting measure to attenuate low-predictor words and increase the weighting of high-predictor words in the body and title of a post.
An offset term was also included which leveled the model's overall prediction for each post and enabled the use of a logistic regression statistical technique to calibrate the model's parameters.
A separate model component was used for the words in the body and title of the post, and it was unclear if \citeauthor{Kuo2011} used the words in the body of the post for his models.

@@

\textcite{Stanley2013} used an ACT-R inspired Bayesian memory model to predict human tagging on the StackOverflow site, but to our knowledge no vector-based holographic memory model has been tested or used.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, it will be interesting to see how a cognitively-plausible vector-based model performs at the task.
Prediction differences between the two models may help reveal ways where the constraints of each model can be adjusted in order to improve accuracy.

@@

There has been a mix of co-occurrence and latent-based models created to predict hashtag use on Twitter, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval theory shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihood of chunks are ranked by that summed activation.
This technique is compensatory and allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.

@@

A modified ACT-R declarative memory retrieval model and random-permutation vector-based model will be evaluated on predicting user-chosen tags for Twitter tweets and StackOverflow posts.
Parameters for each model will be calibrated on a large subset of the Twitter and StackOverflow datasets.
Each model will be tested by evaluating the accuracy of model-chosen tags on a fresh test subset of the datasets.
Accuracy will be assessed by comparing model performance with the human data.

@@

One straightforward way to include a user's prior tag history into a random permutation model is to include ACT-R's base-level activation term ($B_{i}$) as an additional term in the model.
However this may not be the most mathematically appropriate thing to do, since base-level activation is represented as a log odds value,
and the single strength of association term in a random permutation model is computed by a correlation.
It may be more appropriate to somehow attenuate the memory vectors over time,
so that an association between a word in a post and a tag (i.e., a memory vector) that has long passed is no longer included in that memory vector's representation.
I will try these ideas and any others that are discovered during the model development process, and the one that is the most cognitively plausible and accurate will be chosen.

@@

How can word-order information be incorporated into the ACT-R Bayesian model?
Currently ACT-R uses a word co-occurrence matrix that does not include word position.
A co-occurrence is counted if a word and a tag co-occur anywhere in a tweet or post.
However for Twitter in particular, it may be the case that the few words immediately preceding hashtags are highly predictive, and the word position for those words should be included in the model.
So a method to include word order into a Bayesian model will be developed.

@@

The end result of this research will be [1] a better understanding of how a user's past tagging history influences future tag use,
[2] a more thorough evaluation of the strengths, weaknesses, and differences between two cognitively-plausible memory models on large-scale real-world retrieval tasks,
[3] improvements to each memory model where the strengths of each model (word order and user prior likelihood) are incorporated into the other,
and [4] two efficient implementations of the models for making user-customized tag predictions for StackOverflow posts and Twitter tweets.

The tag-recommendation models developed through this research should be immediately relevant to real-world tasks.
If model accuracy is high enough, then the developed models may be used as a foundation for tag recommendation systems that are deployed on Twitter or StackOverflow.
It is also likely that the developed models will scale if deployed to these two sites, since during development they will be tested on a large portion of each site's currently available data.

This research also aims to find task-agnostic memory models that can be applied across a wide range of domains.
As much as possible, the two developed models that are evaluated on the StackOverflow and Twitter datasets will not differ across the datasets.
This should help ensure that the developed models are accurate in general, and can potentially be used as tag recommendation systems for other domains.
Examples of similar tagging tasks are hashtag use on Facebook, flagging (i.e., tagging) Wikipedia articles for content issues or overly-opinionated material,
auto labeling incoming mail and placing it into appropriate folders, and spam filtering.
Having an accurate and efficient co-occurrence memory model that correctly retrieves relevant tags can be applied to a wide variety of real-world tasks.

This research also has numerous components that are relevant to improving our understanding of declarative memory.
It should be emphasized that it has only recently become possible to evaluate psychological theories of declarative memory on large-scale real-world tasks where the theory can be tested on hundreds of millions of data points.
These information-rich large-scale environments provide a unique opportunity to really stress test and explore the impacts of the psychological constraints of each theory
on a much larger scale than has previously been possible.
This environment will allow, for example, overall performance differences between an ACT-R Bayesian retrieval model and a random-permutation vector-based model to be directly compared on two real-world tagging tasks,
which has not been done previously.

@@

Further, the proposed model modifications are aimed at the architectural level, may very well be task independent, and may generalize and improve model fit across other tasks.
Discovering an effective way to represent the time decay of information in a vector-based model could improve model fit on other tasks where the memory model has been used. 
Finding a task-agnostic way to represent word order information in a Bayesian ACT-R model could improve model accuracy when applied to other domains where it seems plausible that participants are utilizing word order.
Introducing, exploring, and evaluating reasonable architectural modifications to two commonly-used memory models is worth the effort:
It will increase our understanding of how the effects of imposing specific architectural constraints on memory models influence what information is retrieved.

>>>>

The ACT-R cognitive architecture \parencite{Anderson2007} contains one of the leading theories of human declarative memory.
The declarative memory component in ACT-R is a Bayesian statistical model.
This is the same type of co-occurrence Naive Bayes statistical model that is prominent in the more general machine-learning field.
When these Bayesian models are used for machine learning, it is common to use a large number of observations to construct the co-occurrence matrix that is the foundation for the model.
The primary reason for this is that the stability of statistical models increase as sample size increases.

However, it is much less common in the cognitive modeling community to use a large number of observations to build up declarative memory when creating ACT-R models.
If a cognitive modeler is using the declarative memory component of ACT-R,
it is common to either construct the co-occurrences by hand, or use a small training set of data to initially build up the declarative memory system.
This approach can and has worked well.
Essentially the modeler is only including the observations in declarative memory that are relevant to the specific task that they are studying.

@@

The work for this proposal will expand on previous work that has tested retrieval models on large-scale datasets.
It will focus specifically on how two state-of-the-art declarative memory retrieval models (ACT-R Bayesian and random permutations) can be improved, by testing these models on two real-world tagging tasks.
One primary objective is to compare the random-permutation vector-based model to ACT-R's declarative memory theory when large datasets are used for each model. 
Another objective is to improve each model, and measure how incorporating the strengths of each model into the other (i.e., modifying model components) influences accuracy.
For example, it is currently unexplored how a vector-based model can be modified to retrieve results that are based not only on context, but also on the prior odds that a particular item in memory will be needed again.
Large-scale datasets will be used throughout the model development and evaluation process.
This provides an ideal testing environment for constraints and assumptions for each theory to be rapidly tested and new model components to be hypothesized and quickly evaluated.

@@

These hashtags relate to a user's goals and interests because they are a form of human-based document tagging \parencite{Chang2010}.
Further, people are using hashtags as a way to create information streams on social media sites \parencite{Kwak2010}.
Twitter users, for example, commonly create and use hashtags for upcoming political events that interest them, such as debates and races \parencite{Diakopoulos2010}.
So if we can predict what hashtags a user is interested in, we have a better understanding of the information streams that they care about.
With that understanding, we can tailor the system to suggest hashtags that they may not yet know about but are of likely interest to them.
We can help aid in their discovery of fresh and relevant information that matches their goals on the site.

@@

These memory retrieval models will also be tested on tag use for StackOverflow posts.
StackOverflow is a question and answer site for computer programming where users ask programming-related questions and fellow members of the community provide answers.
A user with a programming-related question creates a post with their question and tags the post with a few specific programming-related tags. 
User-chosen tags on the StackOverflow site represent the primary topic of the question, such as a specific programming language, tool, software package, or framework.
Some example tags for StackOverflow are \emph{PHP}, \emph{Arrays}, \emph{MVC}, \emph{C\#}, and \emph{Common Lisp}.

@@

ACT-R's declarative memory system places strong constraints on how a user's prior knowledge and experience influences the likelihood that a particular memory item is retrieved \parencite{Anderson2007}.
This decay rate equation formalizes how recency and frequency of hashtag use relate to the prior probability that a hashtag will be retrieved.
However, it is unexplored how a user's prior knowledge should influence retrieval for vector-based models.
I will explore how a user's prior knowledge influences the likelihood that a particular hashtag is chosen for both ACT-R's memory theory and vector-based models.

@@

A user's prior hashtag use will be an essential model component for domains such as Twitter, where the number of possible hashtags is effectively infinite.
In these domains, the model can utilize a user's hashtag history as a way to prune the infinite space of possible hashtags, and generate a much smaller and more manageable set for prediction.
However, not only should the model properly take into account a user's prior hashtag use, but it should also generate new hashtag predictions when a user is most likely choosing a hashtag they have never used before.
The end goal is to have a model that can properly balance the user's tag history with the contextual cues in the post in order to generate an accurate prediction.

@@

ACT-R \parencite{Anderson2007} is a cognitive architecture that formalizes how each cognitive process of the brain (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of that architecture that models the timing, learning, and forgetting processes that make up long-term declarative memory retrieval.
The equations that make up this system can be derived through a rational analysis of long-term memory retrieval.
That is, given the task of retrieving a chunk of information from long-term declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likelihood of needing retrieval again, given the prior history of exposure to the chunk.
These chunk prior probabilities are then adjusted for the current context, so that the posterior probabilities represent the likelihood that a chunk is needed, given prior odds and adjusted by current environment state.

@@

Usually information is lost when the data are restructured into a smaller set of latent dimensions.
However, it was shown that this process actually improves prediction and reduces noise by allowing the frequency count of highly similar concepts (words) to be pooled together and represented by a single dimension.
\textcite{Landauer1997} tested the LSA model on the Test of English as a Foreign Language (TOEFL) task of choosing the best of four possible synonyms to a target word.
Model results were on par with a large sample of applicants to american universities from non-English speaking countries (64.4\% compared to 64.5\%).
Model performance also improved when the original dimensionality of the data was reduced, but only up to a point.
Afterwards further reductions in the dimensionality of the data began to degrade performance.

@@

For vector-based systems, each word is represented by an environment vector $e_{i}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix, which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from position-independent word co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

Recommendation models that attempt to predict a user's chosen hashtag have recently been created and tested for a few social media sites.
Google has even deployed a hashtag-recommendation model to help users properly tag posts on their Google+ social media site \parencite{GoogleKeynote2013}.
A tag-suggestion tool has also been deployed for the \url{http://tex.stackexchange.org} and \url{http://superuser.com} StackExchange sites.
Models for Twitter and StackOverflow have been proposed and tested, but none have yet been deployed.

@@

Several modifications to \textcite{Stanley2013}'s model were made from the standard Bayesian ACT-R declarative memory theory,
so it was more sophisticated than the standard ACT-R model and the model used by \textcite{Kuo2011}.
\citeauthor{Stanley2013} used a data-driven entropy weighting measure to attenuate low-predictor words and increase the weighting of high-predictor words in the body and title of a post.
An offset term was also included which leveled the model's overall prediction for each post and enabled the use of a logistic regression statistical technique to calibrate the model's parameters.
A separate model component was used for the words in the body and title of the post, and it was unclear if \citeauthor{Kuo2011} used the words in the body of the post for his models.

@@

\textcite{Stanley2013} used an ACT-R inspired Bayesian memory model to predict human tagging on the StackOverflow site, but to our knowledge no vector-based memory model has been tested or used.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, it will be interesting to see how a cognitively-plausible vector-based model performs at the task.
Prediction differences between the two models may help reveal ways where the constraints of each model can be adjusted in order to improve accuracy.

@@

There has been a mix of co-occurrence models created to predict hashtag use on Twitter, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval theory shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihood of chunks are ranked by that summed activation.
This technique is compensatory and allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.

@@

The two memory models will be evaluated on predicting user-chosen tags for Twitter tweets and StackOverflow posts.
Parameters for each model will be calibrated on a large subset of the Twitter and StackOverflow datasets.
Each model will be tested by evaluating the accuracy of model-chosen tags on a fresh test subset of the datasets.
Accuracy will be assessed by comparing model performance with the human data.

@@

One straightforward way to include a user's prior tag history into a random permutation model is to include ACT-R's base-level activation term ($B_{i}$) as an additional term in the model.
However, this may not be the most mathematically appropriate thing to do, since base-level activation is represented as a log odds value,
and the single strength of association term in a random permutation model is computed by a correlation.
It may be more appropriate to somehow attenuate the memory vectors over time,
so that an association between a word in a post and a tag (i.e., a memory vector) that has long passed is no longer included in that memory vector's representation.
I will try these ideas and any others that are discovered during the model development process, and the one that is the most cognitively plausible and accurate will be chosen.

@@

How can word-order information be incorporated into the ACT-R Bayesian model?
Currently ACT-R uses a word co-occurrence matrix that does not include word position.
A co-occurrence is counted if a word and a tag co-occur anywhere in a tweet or post.
However, for Twitter in particular, it may be the case that the few words immediately preceding hashtags are highly predictive, and the word position for those words should be included in the model.
So a method to include word order into a Bayesian model will be developed.

@@

This research has numerous components that are relevant to improving our understanding of declarative memory.
It should be emphasized that it has only recently become possible to evaluate psychological theories of declarative memory on large-scale real-world tasks where the theory can be tested on hundreds of millions of data points.
These information-rich large-scale environments provide a unique opportunity to really stress test and explore the impacts of the psychological constraints of each theory
on a much larger scale than has previously been possible.
This environment will allow, for example, overall performance differences between an ACT-R Bayesian retrieval model and a random-permutation vector-based model to be directly compared on two real-world tagging tasks,
which has not been done previously.

@@

Further, the proposed model modifications are aimed at the architectural level, may very well be task independent, and may generalize and improve model fit across other tasks.
Discovering an effective way to represent the time decay of information in a vector-based model could improve model fit on other tasks where the memory model has been used. 
Finding a task-agnostic way to represent word order information in a Bayesian ACT-R model could improve model accuracy when applied to other domains where it seems plausible that participants are utilizing word order.

Additionally, the tag-recommendation models developed through this research should be immediately relevant to real-world tasks.
If model accuracy is high enough, then the developed models may be used as a foundation for tag recommendation systems that are deployed on Twitter or StackOverflow.

Also since the developed models will be task agnostic, they can potentially be used as tag recommendation systems for other domains.
Examples of similar tagging tasks are hashtag use on Facebook, flagging (i.e., tagging) Wikipedia articles for content issues or overly-opinionated material,
auto labeling incoming mail and placing it into appropriate folders, and spam filtering.
Having an accurate and efficient co-occurrence memory model that correctly retrieves relevant tags can be applied to a wide variety of real-world tasks.

The end result of this research will be [1] a better understanding of how a user's past tagging history influences future tag use,
[2] a more thorough evaluation of the strengths, weaknesses, and differences between two cognitively-plausible memory models on large-scale real-world retrieval tasks,
[3] improvements to each memory model where the strengths of each model (word order and user prior likelihood) are incorporated into the other,
and [4] two efficient implementations of the models for making user-customized tag predictions for StackOverflow posts and Twitter tweets. 
Introducing, exploring, and evaluating reasonable architectural modifications to two commonly-used memory models is worth the effort:
It will increase our understanding of how the effects of imposing specific architectural constraints on memory models influence what information is retrieved.
